---
title: "Getting Started with Binomial Package"
author: "Ryan Chien"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(cointoss)
```


## bin_choose()
Used to find the possible combinations of k number of successes in n number of trials

```{r}
bin_choose(7, 2)
```

## bin_probability()
Gives the binomial probability of k number of successes in n number of trials with probability p

```{r}
bin_probability(2, 7, 0.5)
```

## bin_distribution() and plot.bindis()
Creates a bindis object that reflects the properties of a binomial distribution. The object returns a data frame containing the successes and its corresponding probabilities. The plot.bindis() function plots these values on a barplot

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)
```

## bin_cumulative() and plot.bincum()
Creates a bincum object that reflects the properties of a binomial cumulative distribution. The object returns a data frame containing the successes, its corresponding probabilities, as well as its cumulative probabilities. The plot.bincum() function plots these values on a line plot

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```

## bin_var(), print.binvar(), summary.binvar(), and print.summary.binvar()
bin_var() creates a binomial variable with class binvar and with values trials and prob (probability). print.binvar() creates the string representation of the binomial variable listing out its trials and probability values. summary.binvar creates a listed summary object of all the summary values of the binomial variable. 

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum <- summary(bin1)
bin1
binsum
```

## bin_mean(), bin_variance(), bin_mode(), bin_skewness(), and bin_kurtosis()
Each of these functions take in two arguments: trials and probability. And the function returns its respective summary value

```{r}
trials <- 10
p <- 0.3

bin_mean(trials, p)
bin_variance(trials, p)
bin_mode(trials, p)
bin_skewness(trials, p)
bin_kurtosis(trials, p)
```


